\vfill World of Warcraft's New Way to Get You Hooked

### 2013-04-03 paper.tex
1. Changed focus question, no more messin' around.
2. Attempt to make clear the Code section substitution. Don't understand what is meant by "explain".

\section{Focus Question}
Is Blizzard's use of World of Warcraft: Starter Edition ethical?

@@

\subsection{SE Code Section 1.02\\Moderate the interests of the software engineer, the employer, the client and the users with the public good.}
In the next few sections this tenet is broken down into its parts. I will explore the ``interests of the software engineer,'' in this case World of Warcraft's software engineers, the ``interests of ... the employer,'' in this case Blizzard Entertainment, and lastly the ``interests of ... the client and the users,'' the player. Following that will be a discussion of the ``public good.''\\
In this situation SE Code Section 1.02 becomes: ``World of Warcraft's Engineers shall moderate the interests of themselves, Blizzard Entertainment, and the players of World of Warcraft with the public good.''

>>>>

\section{Focus Question}
Is Blizzard's World of Warcraft ethical with its perceived ability to make users addicted?

@@

\subsection{SE Code Section 1.02\\Moderate the interests of the software engineer, the employer, the client and the users with the public good.}
In the next few sections this tenet is broken down into its parts. I will explore the ``interests of the software engineer,'' in this case World of Warcraft's software engineers, the ``interests of ... the employer,'' in this case Blizzard Entertainment since it employs the software engineers, and lastly the ``interests of ... the client and the users,'' the players who use World of Warcraft. Following that will be a discussion of the ``public good.''\\
After substituting the above into the rule, SE Code Section 1.02 becomes: ``World of Warcraft's Software Engineers shall moderate the interests of themselves, Blizzard Entertainment, and the players of World of Warcraft with the public good.''
